A Study on Common Bug Fix Patterns in Rust

### 2022-10-16 sections/methodology.tex
updated stars and commit #

\begin{table}
\caption{\label{table:repos} Target repositories for mining}
\begin{tabular}{l r r r r}
    Project Name & Stars(k) & LOC & \# Commits & Avg. Code Churn \\
    denoland/deno & 84.7 & 146055 & 7730 & 49.22 \\
    tauri-apps/tauri & 48.5 & 50014 & 2929 & 31.67 \\
    alacritty/alacritty & 41.2 & 30124 & 2017 & 27.53 \\
    sharkdp/bat & 36.4 & 9496 & 2392 & 59.13 \\
    starship/starship & 28 & 34888 & 2290 & 25.1 \\
    rust-lang/rustlings & 28.7 & 5067 & 1391 & 8.92 \\
    meilisearch/meilisearch & 28.6 & 25981 & 3849 & 279.7 \\
    sharkdp/fd & 24.2 & 6542 & 1025 & 12.2 \\
    swc-project/swc & 23.5 & 346501 & 5205 & 44.34 \\
    yewstack/yew & 23.2 & 44295 & 2239 & 21.79 \\
    xi-editor/xi-editor & 19.5 & 39292 & 2104 & 28.67 \\
    AppFlowy-IO/AppFlowy & 25.9 & 57646 & 2600 & 29.49 \\
    firecracker-microvm/firecracker & 18.9 & 82021 & 3536 & 58.26 \\
    nushell/nushell & 20.3 & 163562 & 5922 & 22.38 \\
    ogham/exa & 18.9 & 10852 & 1558 & 11.99 \\
    SergioBenitez/Rocket & 18.2 & 68952 & 2127 & 19.75 \\
    rustdesk/rustdesk & 27.7 & 48115 & 1664 & 72.81 \\
    tokio-rs/tokio & 17.2 & 121400 & 3006 & 28.87 
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{\label{table:repos} Target repositories for mining}
\begin{tabular}{l r r r r}
    Project Name & Stars(k) & LOC & \# Commits & Avg. Code Churn \\
    denoland/deno & 85.9 & 146055 & 8026 & 49.22 \\
    tauri-apps/tauri & 52.5 & 50014 & 3041 & 31.67 \\
    alacritty/alacritty & 42.4 & 30124 & 2036 & 27.53 \\
    sharkdp/bat & 37.6 & 9496 & 2457 & 59.13 \\
    starship/starship & 29.3 & 34888 & 2379 & 25.1 \\
    rust-lang/rustlings & 30.6 & 5067 & 1466 & 8.92 \\
    meilisearch/meilisearch & 30.2 & 25981 & 4029 & 279.7 \\
    sharkdp/fd & 24.9 & 6542 & 1068 & 12.2 \\
    swc-project/swc & 24.2 & 346501 & 5884 & 44.34 \\
    yewstack/yew & 24.5 & 44295 & 2280 & 21.79 \\
    xi-editor/xi-editor & 19.6 & 39292 & 2105 & 28.67 \\
    AppFlowy-IO/AppFlowy & 28.4 & 57646 & 3321 & 29.49 \\
    firecracker-microvm/firecracker & 19.6 & 82021 & 3620 & 58.26 \\
    nushell/nushell & 21.1 & 163562 & 6088 & 22.38 \\
    ogham/exa & 19.5 & 10852 & 1558 & 11.99 \\
    SergioBenitez/Rocket & 18.7 & 68952 & 2135 & 19.75 \\
    rustdesk/rustdesk & 30.2 & 48115 & 2620 & 72.81 \\
    tokio-rs/tokio & 17.9 & 121400 & 3101 & 28.87 
\end{tabular}
\end{table}
